Frequency of galaxy pairs in the Illustris and Illustris TNG cosmological simulations

### 2022-11-04 paper/pears.tex
i promise i changed something
pls compile?
paper template w light outlining

\documentclass[twocolumn]{aastex63}

\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\msun{\rm{M}_{\odot}}
\newcommand\ID{\textit{Illustris-Dark}}
\newcommand\IH{\textit{Illustris-Hydro}}
\newcommand\SUBFIND{\texttt{SUBFIND}}
\definecolor{mypink}{RGB}{232,132,161}
\newcommand{\kc}[1]{\textcolor{mypink}{\textbf{#1}} }
\newcommand{\gb}[1]{\textcolor{olive}{\textbf{#1}} }
%\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
%\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{soul}
% \usepackage{amssymb}

% \graphicspath{{./}{figures/}}
% \graphicspath{{../}{figures/}}

% \shorttitle{Sample article}
% \shortauthors{Schwarz et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Occurance rate of galaxy pairs across cosmic time:\\ Local Group analogs in a cosmological context}
\correspondingauthor{Katie Chamberlain}
\email{katiechambe@email.arizona.edu}

\author[0000-0001-8765-8670]{Katie Chamberlain}
\affil{Steward Observatory, University of Arizona\\
933 North Cherry Avenue\\
Tucson, AZ, 85721, USA}
\author{Gurtina Besla}
\affil{Steward Observatory, University of Arizona\\
933 North Cherry Avenue\\
Tucson, AZ, 85721, USA}
\begin{abstract}

  % \textbf{Context} 
  Dwarf galaxies are extremely common at all redshifts and often exhibit morphological disturbances that do not primarily result from galaxy mergers. As such, pair fractions, rather than morphological indicators (asymmetry, concentration) are needed to infer dwarf galaxy  merger rates from observational surveys.
  However, in contrast to massive galaxies ($5\times 10^9\leq$ $\rm M_{prim,*} \leq 1\times 10^{11} \msun$), pair fractions for dwarf galaxies ($10^8 < \rm M_* < 5 \times 10^9 \msun$) have been theoretically constrained only at low redshift.
  % \\\textbf{Aims}
  We aim to quantify the occurence rates and kinematics of isolated dwarf and massive galaxy pairs from $z=0-4$ in the Illustris and IllustrisTNG cosmological simulations.
  % \\\textbf{Methods} 
  Dwarf and massive subhalo pairs are identified in each snapshot of the Illustris \texttt{SUBFIND} catalogs. 
  % \\\textbf{Results} 
  We find that roughly 8-10\% of dwarf galaxies will have major companion (stellar mass ratio $>1:4$) at $z=0$, increasing steadily before plateauing in \ID(\IH) at 16\%(12\%) by $z\sim 2$. The occurence rate of dwarf galaxies with minor companions (stellar mass ratios between $1:10$ and $1:4$) is roughly constant at $\sim 2.5\%$ from $z=1-4$. In contrast, the occurence rate of major and minor massive galaxy pairs remains approximately constant across time, as massive galaxies have a major (minor) companion $\sim18\%$ ($\sim14\%$) of the time.
  % \\\textbf{Conclusions} 
  This suggests that the hierarchical evolution of dwarf galaxies may proceed differently than that of massive galaxies. LMC-SMC mass analogs (dwarf minor pairs) are twice as common at redshifts greater than 2, but the present day LMC-SMC system is dynamically rare at all redshifts (in terms of pair separation and velocity). The M31-M33 pair is dynamically typical of massive minor pairs at $z\approx0$, while the MW-LMC has unusually high velocities and low relative separations for a major massive pair at low redshift. Baryonic physics impacts the occurence rate of galaxy pairs and systematically changes the kinematics of dwarf pairs, suggesting observations of dwarf galaxy pairs can be used to test subgrid physics in cosmological simulations.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%
Galaxy mergers are responsible for many physical processes that shape galactic evolution, including triggered star formation~\citep{mihos96, hopkins13, patton20,hani20}, increased AGN activity~\citep{hopkins08,comerford15,ellison19}, and galaxy morphology~\citep[e.g.,][]{rg17}. Dwarf galaxies  make up a majority of the galaxy population at all redshifts (REF) and are also expected to undergo interactions and merge. Such processes may be important to understand the growth and evolution of intermediate mass black holes, which are often found to be ``wandering" in low mass galaxy hosts~\citep{stemo20,reines20}. Despite the ubiquity of dwarf galaxies in the universe, we do not have a clear path to constrain the merger rates of these systems observationally or to place known interacting dwarf galaxy systems (stellar mass $1\times10^8<M_* < 5\times10^9\msun$) in a cosmological context.

Massive galaxy ($M_* > 5\times10^9\msun$) mergers and interactions can be observationally identified using methods like asymmetry and concentration measures~\citep{conselice2000, lotz04}. Numerous studies have used these measures to study the merger and interaction rates of massive galaxies as a function of time~\citep[e.g.,][]{lotz11,casteels14}.

However, \citet{martin21} showed that mergers only account for 10\% of morphological disturbances in dwarfs, and that a majority of their morphological disturbances derive from non-merger interactions, such as gas inflows/outflows, close passages, and fly-bys. This means that the typical methods of classifying interactions and mergers for massive galaxies are unlikely to be robust in lower mass regimes. This is particularly true at high redshift, when gas accretion along filaments is expected to be more significant~\citep{keres09}. Thus, it is critical to establish an alternative, cosmologically consistent, way to determine merger and interaction rates for dwarf galaxy pairs from observations.

Another observational technique to determine merger/interaction rates relies upon the pair fraction: the ratio of the number of host galaxies with a companion to the number of potential hosts. Pair fractions for massive galaxies have been measured observationally as a function of time~\citep[e.g.,][]{lotz08,conselice09}, and calibrated against theoretical simulations to determine observability timescales that enable the translation of pair fractions to merger rates \citep{lotz11,kaviraj15,snyder17,qu17,oleary21b}.
In contrast, pair fractions for dwarf primaries are only starting to be measured at high redshift \citep[e.g.][]{ventou17} and have only been studied with small sample size or calibrated against simulations at low redshift \citep{besla18, casteels14,stierwalt15, pearson18}. Thus we are currently missing a theoretical framework to interpret future high redshift observations of dwarf pairs, i.e. with \textit{JWST}. In this study, we quantify the dwarf galaxy pair fraction as a function of time out to $z\sim$4, and compare these results to the massive galaxy pair fraction, using the N-body and hydrodynamic \textit{Illustris-1} cosmological simulations~\citep{vogelsberger14A,nelson15}.

There are examples of galaxy pairs involving dwarf galaxies in our Local Group, including the M31-M33, MW-LMC, and the LMC-SMC (Magellanic Clouds; MCs) systems. The frequency of such pairs have been studied extensively observationally and theoretically at low redshift.
In SDSS DR7, it is found that 11\% of MW/M31-like objects have one massive satellite (LMC/M33 analog) within 150 kpc and 300 km s$^{-1}$~\citep{liu11}. Within 250 kpc, the frequency increases to 42\% (Tollerud 2011). % , robotham12
This is in agreement with $\Lambda$CDM predictions \citep{busha11, bk11, patel17a, gonzalez13}. 
% check gonzalez
Furthermore, 4-6\% of LMC/M33 analogs in both SDSS and cosmological simulations are expected to have a companion at least as massive as an SMC in the field \citep{besla18, sales11}. %% ADD SALES RESULTS ?      
% add how defined here

However, we do not how common these pair configurations are as a function of time in the $\Lambda$CDM framework, leaving open the question as to whether our Local Group is unique in time. 
Recent advances in astrometry have furthermore enabled the measurement of 6D phase space information for these Local Group galaxy pairs.  
In this study, we will examine whether not only the frequency, but also the dynamics of pairs in our Local Group are unique \textit{across cosmic time}.
% HOW DO MASSIVE PAIRS SCALE TO DWARF REGIME

The Local Group also contains a massive major galaxy pair (stellar mass ratio $>$1:4), the MW-M31. For low redshift (z$<$ $\sim$.1) massive galaxies (M$_\ast > 10^{10}$ M$_\odot$), the fraction of major pairs are expected to increase as a function of mass \citep{casteels14}, resulting in major merger rates that rise  with higher mass~\citep{rg15,ventou17,oleary21b}. Additionally, the fraction of major pairs is also measured to increase with increasing redshift~\citep{deravel09,bundy09,duncan19}. In particular \citet{duncan19} find no strong evolution in the relative number of minor to major mergers for massive hosts out to z$<$3. But it is unclear whether these trends for the frequency of major pairs will be the same if the host mass is in the dwarf galaxy regime.

It is important to study the dwarf and massive host regimes separately, as baryonic physics, including gravitational tides, star formation, and outflows, impacts the growth of dwarf galaxies more strongly~\citep{bullockbk17,jeon19,jeon21}. For example, it has been shown that baryonic physics implemented in the \IH\ simulation suppresses the abundance of low mass subhalos ($\leq$10$^{10}\msun$), but such a suppression is not present for massive halos~\citep{chua17}. Thus, the pair fractions and dynamics of dwarf major and minor pairs may change drastically between the dark-matter-only and full-physics simulations, with less differences for massive  pairs. In this study, we illustrate that the impact of baryonic physics on the growth of low mass halos in cosmological simulations may be directly testable with pair fraction observations.

Here we present the first cosmologically motivated constraints on the dwarf pair fraction for major and minor pairs as a function of time. We compare these results to those found for massive major and minor pairs, and address the differences in expected pair fractions between the N-body and full hydrodynamic simulations. This work will furthermore, self-consistently, place known galaxy pairs in our Local Group in a cosmological and temporal context.  In Sec.~\ref{sec:methods}, we introduce the simulations and selection criteria used to perform the analysis of our sample of pairs. In Sec.~\ref{sec:results}, we present the results of this pair fraction study, including preliminary results on the kinematics of dwarf pairs over cosmic time. In Sec.~\ref{sec:discussion}, we discuss the implications of our results on interpretations of future surveys, and what this could mean for constraints of feedback mechanisms in cosmological simulations. In Sec.~\ref{sec:conclusions} we present a summary of the main conclusions of this work, including expected pair fractions for dwarf and massive galaxy pairs.

%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:methods}
%%%%%%%%%%%%%%%%%
Our sample of dwarf galaxy pairs and massive galaxy pairs from cosmological simulations was chosen following a strict set of selection criteria. In Sec.~\ref{sec:simData} we will detail the simulations from which we collected our data, Sec.~\ref{sec:abundanceMatching} explains the abundance matching prescription used to associate dark matter halos with stellar masses, and Sec.~\ref{sec:selectionCrit} outlines the isolation and mass criteria used to identify our sample.

\subsection{Simulation data}\label{sec:simData}
We utilize data from the \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15}, a set of N-body and hydrodynamic cosmological simulations, to statistically analyse the occurrence rates of dwarf and massive dark matter subhalo pairs over cosmic time. In particular, we are using the highest resolution dark matter only simulation, \textit{Illustris-1-Dark}, and the  full hydrodynamic simulation, \textit{Illustris-1} (hereafter \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively, see Table~\ref{table:illustris}).
Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of $106.5^3$ Mpc$^3$. The Illustris simulations use a cosmology that is consistent with \textit{WMAP-9} ~\citep{hinshaw13}: $\Omega_m = 0.2726$, $\Omega_\Lambda = 0.7274$, $\Omega_b = 0.0456$, $\sigma_8 = 0.809$, $n_s=0.963$, and $h=0.704$.

% Maybe doesn't need whole paragraph but, about dark vs. hydro
We are utilizing data from both \textit{Illustris-Dark} and \textit{Illustris-Hydro} to study the effect of baryonic content on the subhalos. As dwarf subhalos have more shallow dark matter potentials than their more massive counterparts, they are more likely to be subject to disruption caused by baryonic feedback at higher redshifts, which may result in fewer low mass subhalo pairs in \textit{Illustris-Hydro}.

% Subfind paragraph: 
We use catalogs of dark matter halos and their associated subhalos identified in each simulation using the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}. Dark matter halos were identified using the Friends-of-Friends (FoF) algorithm ~\citep{davis85}, which links particles that have separations less than $0.2d$, where $d$ is the mean inter-particle separation. Each FoF group, which we will further refer to as a ``group", was further divided into over-dense and gravitationally bound dark matter subhalos.

% Sublink paragraph:
In order to trace the growth and histories of our subhalos, we are using the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data. These merger trees provide information about the kinematics and mass growth of subhalos in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}, and in particular will be used to provide the maximal masses of each of the subhalos we investigate.

The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\msun$, such that each of our halos are resolved into at least 130 particles in \textit{Illustris-Dark} and 150 particles in \textit{Illustris-Hydro}. 
% \kc{add explanation for why 100 particles is good enough for the resolution we're looking for.}

\begin{table}[htb]
\begin{tabular}{lll}
 & Illustris-Dark & Illustris-Hydro \\\hline\hline
 L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 \\
m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ \\\hline
\end{tabular}
\caption{\label{table:illustris}Parameters of the Illustris simulations used in this analysis.}
\end{table}
% when i start using TNG can add this!
% \begin{table*}[htb]
% \begin{tabular}{lllll}
%  & Illustris-Dark & Illustris-Hydro & IllustrisTNG-Dark & IllustrisTNG-Hydro\\\hline\hline
%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\\hline
% \end{tabular}
% \caption{Parameters of the Illustris simulations used in this analysis.}
% \end{table*}

\begin{table*}[htb]
  \begin{center}
    \begin{tabular}{lcc}
     & Dwarf Pairs & Massive Pairs \\\hline\hline
    Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
    % Subhalo Max Mass &  &  \\
    Subhalo Current Mass & $>1\times10^{10} \msun$ & $> 5\times10^{11} \msun$ \\
    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \msun$\\\hline
    \end{tabular}
    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
  \end{center}
    \end{table*}

\subsection{Abundance matching}\label{sec:abundanceMatching}
Although \textit{Illustris-Hydro} provides stellar masses for all subhalos, however these reported masses are higher than observations suggest~\citep{genel14}. We assign stellar masses to dark matter halos in a consistent way between both \ID\ and \IH using the abundance matching (AM) prescription of \citet{moster13} to associate each dark matter halo with a stellar mass.

The AM relationship at low stellar masses has a large spread, thus a subhalo with a dark matter halo mass of $10^{11}$ may be associated with a stellar mass anywhere between $1.2\times10^{8} - 5\times10^{9}\rm M_\odot$, as can be seen in Fig.~\ref{fig:abundanceMatching}.

There are two inputs to the AM relationship: dark matter mass and redshift. As shown recently by \citet{munshi21}, the relationship between stellar mass and peak halo mass of dwarf subhalos in the Marvel and Justice League simulations is much tighter than the relationship between the stellar mass and halo mass of subhalos at $z=0$. We use the maximal dark matter mass of the halo to ensure that the stellar mass associated with each subhalo reflects the shape of the dark matter profile in the inner regions of the subhalo, thus preventing us from assigning very low stellar masses to halos that have been stripped of %a lot of 
their outer dark matter mass by recent interactions. We evaluate the AM relation using the redshift of the halo at the snapshot that we are interested in, rather than the redshift of the halo at its maximal mass, in order to account for ongoing star formation past peak halo mass.

For the collection of subhalos identified at each snapshot of the simulation, the stellar masses are drawn from the gaussian sampled AM relation. We thus generate 50 realizations for the stellar mass distribution of the same subhalo population in order to account for uncertainties in the AM relation. Each realization is treated as an independent sample of galaxies, where computed properties (stellar masses, relative speeds, etc) are averaged over each realization. We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
  \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$. Note that at halo masses below $\sim10^{12} \msun$, there is more spread in stellar mass at fixed halo mass compared to halos with $\rm M_{H} > \sim10^{12} \msun$. This effect is illustrated by the vertical lines at $10^{11}\msun$ and $10^{13}\msun$. %\gb{might be useful here to indicate with horizontal lines the stellar mass range for the dwarf systems and the massive galaxy systems} 
  }
\end{figure}

\subsection{Selection criteria}\label{sec:selectionCrit}
In this section, we will outline the selection criteria used to identify dwarf subhalo and massive subhalo pairs in the \ID\ and \IH\ simulations. In short, we first make a series of mass cuts on the group mass to constrain the masses of the halos that may be contained in the group and to ensure that the systems are relatively isolated. Then, the subhalos of each identified isolated group undergo further mass cuts until we are left with a sample of both dwarf and massive subhalo pairs. A summary of the mass criteria used for our selection can be found in Table~\ref{table:mass}.

\subsubsection{Isolation}
We are interested in the occurrence rates of subhalo pairs in pristine environments to ensure that the dynamics of the subhalos in groups are unaffected by nearby massive perturbers.

FoF groups are large collections of nearby associated particles throughout the Illustris simulation. As there is no boundedness criteria for these groups, we wanted to ensure that pulling pairs of subhalos from FoF groups would yield a sample of subhalos that were dynamically unperturbed by more massive nearby structures. We calculated the isolation fraction 
\begin{equation}
f_{\rm iso} = N_{\rm Hill} / N_{\rm FoF}
\end{equation}
where $N_{\rm Hill}$ is the number of pairs of subhalos that satisfy the Hill radius criterion (see Appendix~\ref{app:hill}), and $N_{\rm FoF}$ is the number of pairs from FoF groups, and found that $>99.8\%$ of all pairs identified in FoF groups are considered isolated by the more stringent Hill radius criterion. We thus used these FoF groups as a proxy for isolation, and considered \textit{all} pairs from FoF groups isolated.

\subsubsection{Group mass cuts}
% why group cuts
We first make a series of cuts on the group masses reported in the \ID and \IH catalogs at each snapshot out to $z\sim12$. Since we are interested in subhalo pairs in two different mass regimes, we will use different mass criteria to isolate groups that may contain dwarf pairs, and groups that may contain more massive galaxy pairs. As mentioned, we do not search for dwarf pairs in massive groups 
since the central subhalos of these more massive groups would perturb the dwarf system.

% actual numerical values of 
Group mass cuts are performed on the group mass provided in the SUBFIND catalogs, \texttt{Group\_M\_TopHat200}, which is the total mass enclosed in a sphere whose mean density is $\rho_c \Delta_c$. The {\bf dwarf groups} must have a group mass $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ while {\bf massive groups} have mass $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$. These dwarf and massive group masses are roughly representative of Magellanic Cloud analogs~\citep{besla12,moster13} and Local Group analogs respectively~\citep{vdm12ii}.

In addition to %overall 
group mass cuts, we ensure that each group has at least one subhalo that satisfies the following properties:
\begin{itemize}
    \item \textit{dwarf} - maximal halo mass is $8\times10^{10} < \rm M_{\rm max} < 5\times10^{11} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 1\times10^{10} \rm M_\odot$
    \item \textit{massive} - maximal halo mass is $1\times10^{12} < \rm M_{max} < 4\times10^{12} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 5\times10^{11} \rm M_\odot$. 
\end{itemize}
This ensures that each group has at least one subhalo that will serve as a primary galaxy for the catalog after stellar mass cuts are applied (Sec.~\ref{sec:primaries}).

We only consider subhalos in each of these groups that have subhalo masses $M_{H}>10^9M_{\odot}$ at the given snapshot. This ensures that each dwarf pair will consist of subhalos that are resolved into more than 100 dark matter particles at the snapshot of interest.

In practice we find that some low mass groups consist of a set of subhalos with only one or two subhalos with mass above our lower mass threshold of $10^9\msun$, while the remaining subhalos have lower mass. We refer to these types of groups as ``One Subhalo'' and ``Two Subhalo'' groups respectively, since they contain either one or two candidate primaries. Groups with three or more subhalos passing this lower mass threshold are called ``Three+ Subhalo'' groups.

\begin{table*}[htb]
  \begin{center}
\begin{tabular}{ccccc|cccc}
    & \multicolumn{4}{c}{Dwarfs} & \multicolumn{4}{c}{Massive} \\\hline\hline
    z = &0&1&2&4&0&1&2&4 \\ \hline
    Isolated Groups & \# & \# &\# &\#&\#&\#&\#&\#\\
Primaries &  & &&&&&& \\
Pairs &  & &&&&&& \\
Major Pairs &  & &&&&&& \\
Minor Pairs &  & &&&&&& \\
Minor+ Pairs &  & &&&&&& \\\hline
\end{tabular}
\end{center}
\caption{\label{table:counts}\kc{Placeholder for now} Number of groups, primaries, and pairs}
\end{table*}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
    \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}. The linestyle represents the different types of groups where the primaries are identified. The dotted (dashed) lines show the number of primaries in
    groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
    groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$. We find that \textit{Illustris-Hydro} has significantly many more primaries in single and double-subhalo groups, which may be a result of different dwarf merger rates in the two simulations. Since there are many more single-subhalo dwarf groups in \textit{Illustris-Hydro}, the fraction of primaries with a companion will be significantly suppressed compared to \textit{Illustris-Dark}.
    There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
  \end{figure}

\subsubsection{Dwarf and Massive Primaries}\label{sec:primaries}
Dwarf and massive primaries are defined to be the most massive subhalo in each group with the following properties:
\begin{itemize}
  \item \textit{dwarf} - stellar mass between $10^8 \leq \rm M_{prim,*} \leq 5\times 10^9 \msun$
  \item \textit{massive} - stellar mass between $5\times 10^9 \rm M_{prim,*} \leq 1\times 10^{11} \msun$.
\end{itemize}
We make mass cuts using the stellar masses of the subhalos in order to best compare our results with observational studies. %as this is the data that we will be collecting observationally. Thus, making cuts on the stellar masses of these subhalos allows us to more directly apply our results to observational studies.

The average number of dwarf and massive primary subhalos  %at each of the considered redshifts 
is plotted as a function of redshift in Fig.~\ref{fig:counts}.%, and 
A subset of this data can be found in Table~\ref{table:counts}. Also plotted is the number of primaries in groups with the marked number of companions.

We find that the number of dwarf primaries increases from $z=4$ to about $z\sim0.5$, at which point the number of primaries decreases by approximately 15\% approaching $z=0$. There are significant differences in the number of dwarf primaries that belong to One- and Two-Subhalo Groups in \ID\ and \IH. \IH\ boasts about $2\times$ more primaries in One-Subhalo groups, 1.5-2$\times$ more primaries in Two-Subhalo Groups, and ~0.6$\times$ fewer Three-Subhalo groups than \ID.

The number of massive primaries increases consistently from high to low redshift. There are very few massive groups with only one or two large ($\rm M_{H} > 10^9\sun$) subhalos, since groups of this mass scale typically host at least one large subhalo and its companions and satellites. Thus, almost 100\% of the massive primaries reside in ``Three-Subhalo'' groups.

\subsubsection{Pairs}
The different pair types are defined to contain a dwarf or massive primary subhalo with a secondary subhalo:
\begin{itemize}
    \item \textit{Major Pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/4 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1$.
    \item \textit{Minor pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/10 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
    \item \textit{Minor+ Pairs}: with stellar mass $M_{\rm sec,*}$ such that $M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$. This set of pairs \textit{includes} the whole set of minor pairs, but also includes pairs whose mass ratio is less than 1/10. 
\end{itemize}
The MCs, as well as the MW+LMC system and M31+M33 system, have a stellar mass ratio of approximately 1/10, and thus would be classified as minor pairs according to our analysis. All pairs must be separated by at least 15 physical kpc so that the pairs are well resolved into individual component subhalos in \SUBFIND.

%
%%
%%%
%%%%
%%%
%%
%

%%%%%%%%%%%%%%%%%
\section{Results}\label{sec:results}
%%%%%%%%%%%%%%%%%
After collecting our sample of dwarf and massive pairs, we analyzed the frequency of occurrence as well as their properties, such as mass ratio and average kinematics of the pairs, as a function of time. By comparing results for groups identified in \ID\ and \IH , we can compare the effect that feedback prescriptions may have on the formation of low mass dwarf pairs vs. massive pairs, and search for differences in their kinematics, which ultimately dictate their merger rates.

Although we collected pairs out to redshift $z\sim12$, the number of identified primaries drops significantly approaching $z\sim4$. As such, the following analysis will focus only on a redshift range of $z=0-\sim4$, where the statistics are more meaningful. In Sec.~\ref{sec:ratios}, we will discuss the stellar, current halo, and maximum halo mass ratios for our sample, which will enable us to examine the mass evolution of these systems. In Sec.~\ref{sec:pairFracs}, we present the main data product of this paper, namely the pair fractions for dwarf and massive major and minor pairs in \ID\ and \IH. In Sec.~\ref{sec:kinematics}, we discuss our findings on the kinematics of our population of pairs.

%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
% description of the stellar and halo mass evolution
\subsection{Stellar and Halo Masses and Ratios}\label{sec:ratios}
\begin{figure*}[htb]
    \centering
    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
    \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift. (Top) Mean stellar masses of dwarf pair primaries, where the shaded regions indicate the $1\sigma$ spread computed over 50 realizations of AM relation per snapshot. %dwarf pairs. 
    (Bottom) The same as Top panels, but for the primaries of massive pairs. For dwarf pairs, the average primary stellar mass of minor pairs is much higher than for major pairs, although is roughly the same for massive pairs. The average primary stellar mass increases as a function of time for both dwarf and massive pairs. There are no major differences between the primary stellar masses in \ID\ and \IH, which indicates that the max subhalo masses of the primaries in each of the simulations is roughly equivalent.
     \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
\end{figure*}

>>>>

\documentclass[twocolumn]{aastex631}

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}

\definecolor{pink}{RGB}{232,132,161}
\definecolor{yellow}{RGB}{255,213,0}

\newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
% \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
% \newcommand{\e}[1]{\textcolor{yellow}{\textbf{: #1}} }

\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}

\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
\newcommand{\mud}{\ensuremath{\mu_\delta}}
\newcommand{\mua}{\ensuremath{\mu_\alpha^*}}
\newcommand{\bov}{\ensuremath{\boldsymbol{v}}}
\newcommand{\boldx}{\ensuremath{\boldsymbol{x}}}
\newcommand{\vtrav}{\ensuremath{\bov_{\rm travel}}}
\newcommand{\xtrav}{\ensuremath{\boldx_{\rm travel}}}
\newcommand{\pos}[2]{\ensuremath{\boldx_{\rm #1 \to #2}}}
\newcommand{\vel}[2]{\ensuremath{\bov_{\rm #1 \to #2}}}
\newcommand{\mwbary}{\ensuremath{\textrm{MW}_\textrm{bary}}}
\newcommand{\mwouter}{\ensuremath{\textrm{MW}_\textrm{halo}}}
\newcommand{\mwdisk}{\ensuremath{\textrm{MW}_\textrm{disk}}}
\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}

% Style tweaks
% \renewcommand{\twocolumngrid}{\onecolumngrid}
% \setlength{\parindent}{1.1\baselineskip}
% \sloppy\sloppypar\raggedbottom\frenchspacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\shorttitle{Frequency of galaxy pairs}
\shortauthors{Chamberlain et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
\input{math_definitions.tex}

% Affiliations
\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
    Tucson, AZ 85721, USA}

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{
  Frequency of galaxy pairs in the Illustris and Illustris TNG cosmological simulations
}

\author[0000-0001-8765-8670]{Katie~Chamberlain}
\affiliation{\affuofa}

\author[0000-0003-0715-2173]{Gurtina Besla}
\affiliation{\affuofa}

\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
\label{sec:methods}
\begin{itemize}
  \item Introduce simulations
  \item outline selection steps
  \item dwarf pairs
  \item massive pairs
  \item include table with parameters used for pairs
  \item plots
    \begin{itemize}
      \item distribution plots
      \item counts plots
    \end{itemize}
\end{itemize}

% selection criterion
\begin{table*}[htb]
  \begin{center}
    \begin{tabular}{lcc}
     & Dwarf Pairs & Massive Pairs \\\hline\hline
    Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
    % Subhalo Max Mass &  &  \\
    Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \Msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \Msun$\\\hline
    \end{tabular}
    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
  \end{center}
    \end{table*}

% equivalent snapshot table
\begin{table}[]
  \centering
  \begin{tabular}{l|cc}
    \hline \hline
   & Illustris & TNG  \\ 
  \hline
  z = 0   &   135  &   99   \\
  z = 1   &   85   &   50   \\
  z = 2   &   68   &   33   \\
  z = 3   &   60   &   25   \\
  z = 4   &   54   &   21   \\
  \hline \hline
  \end{tabular}
  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-4$.}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Conclusions}
\label{sec:summary}

%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{refs}{}
\bibliographystyle{aasjournal}
